ms_figures

### 2024-05-02 ms_figures.Rmd
ms figures labels fixed based on pdf journal size requirements

```{r load_data}
# Set directories
datadir <- "qa/manuscript_archive/manuscript_inputs"
outdir <- "qa/manuscript_archives/figures"
```

@@

fig1a <- fig1a_data %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports\n(mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 6)
        )

@@

ggsave(file.path(outdir, "fig1.png"))
# ggsave(file.path(outdir, "fig1.pdf"), device = "pdf", height = )
```

@@

marine_cap_stacked_bar <- marine_cap_sciname %>%
  mutate(common_name = case_when(
    common_name == "alaska pollock(=walleye poll.)" ~ "alaska pollock",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    panel.spacing = unit(2, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_text(size = 8),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

@@

marine_cap

# ggsave(file.path(outdir, "marine_cap_map_bar.png"), width = 6, height = 3, dpi = 300, units = "in", device = "png")
```

@@

marine_aqua

@@

inland_cap_stacked_bar <- inland_cap_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "\nray-finned fishes",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile perch" ~ "\nnile perch",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(2, "mm"),
    plot.margin = margin(r = 5, l=-10, b=-5, unit="mm")# unit(c(, 5, 0, -10), "mm")
  )

@@

inland_aqua_stacked_bar <- inland_aqua_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "\nray-finned fishes",
    common_name == "striped catfish" ~ "\nstriped catfish",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile tilapia" ~ "\nnile tilapia",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  mutate(region = case_when(
    region == "North America" ~ "N. America",
    region == "South America" ~ "S. America",
    TRUE ~ region
  )) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "", fill = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(size = 8),
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = element_text(size = 8),
    legend.key.size = unit(3, "mm"),
    legend.box.margin = margin(l = -25, unit = "mm"),
    legend.margin = margin(t = -7, b = 0, unit = "mm"),
    panel.spacing = unit(2, "mm"),
    plot.margin = unit(c(0, 5, 0, -10), "mm")
  )

@@

ggsave(file.path(outdir, "test.png"), width = 6, height = 3, dpi = 300, units = "in", device = "png")
```

@@

ggsave(file.path(outdir, "fig2.png"), width = 9, height = 13, dpi = 500, unit = "in", device = "png")
```

@@

ggsave(file.path(outdir, "fig3.png"))
```

@@

ggsave(file.path(outdir, "fig4.png"))
```

@@

```{r regional_sankey, fig.height = 3, fig.width = 3}
regional_artis <- read.csv(file.path(datadir, "si_fig_1_data.csv"))

@@

marine_cap_regions$node <- factor(marine_cap_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

marine_cap_p <- marine_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(t=-0.5, r=-10, b=-1, l=-18), unit = "mm")
    )

@@

marine_aqua_regions$node <- factor(marine_aqua_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

marine_aqua_p <- marine_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(t=-0.5, r=-10, b=-1, l=-18), unit = "mm")
    )

@@

inland_cap_regions$node <- factor(inland_cap_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

@@

inland_aqua_regions$node <- factor(inland_aqua_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "South America", "North America",
                                         "Africa"))

@@

ggsave(file.path(outdir, "si_fig1.png"))
```

@@

ggsave(file.path(outdir, "si_fig2.png"))
```

@@

ggsave(file.path(outdir, "si_fig3.png"))
```

@@

ggsave(file.path(outdir, "si_fig4.png"))
```

@@

dom_source_by_habitat_method_p <- dom_source_by_habitat_method %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine capture", "inland capture",
                                                            "marine aquaculture", "inland aquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = live_weight_t / 1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  theme_bw() +
  labs(x = "", y = "Live weight\nmillion tonnes", fill = "Source") +
  facet_wrap(~dom_source) +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 10),
    panel.spacing = unit(5, "mm"),
    legend.box.margin=margin(t = -15)
  )

@@

ggsave(file.path(outdir, "si_fig5.png"))
```

@@

ggsave(file.path(outdir, "si_fig6.png"))
```

@@

ggplot() +
  geom_line(data = artis_ts, aes(x = year, y = product_weight_t, color = hs_version), linetype = "dashed", linewidth = 1) +
  geom_line(data = custom_ts, aes(x = year, y = product_weight_t, color = hs_version), linewidth = 0.5, linetype = "solid") +
  scale_color_manual(
    values = c("Custom ARTIS Time series" = "black", "HS96" = "#741A32", "HS02" = "#B34232", "HS07" = "#D38F35", "HS12" = "red", "HS17" = "#114F59")
  ) +
  labs(x = "Year", y = "Product Weight (tonnes)", color = "HS Version") +
  theme_bw() +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 10)
  )

ggsave(file.path(outdir, "si_fig7.png"))
```

>>>>

```{r load_data}
# Set directories
datadir <- "qa/manuscript_archive/manuscript_inputs"
outdir <- "qa/manuscript_archive/figures"
```

@@

fig1a <- fig1a_data %>%
  mutate(habitat_method = factor(habitat_method, 
                                 levels = c("marine capture", "inland capture", 
                                            "marine aquaculture", "inland aquaculture", "unknown"))) %>%
  ggplot(aes(x = year, y = live_weight_t/1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  labs(y = "Exports\n(mil. t, live weight)", fill = "Source", x = "") +
  theme_bw() +
  theme(legend.position = "bottom",
        text = element_text(size = 10),
        axis.title.y = element_text(size = 12),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        legend.title = element_text(size = 7),
        legend.text = element_text(size = 6)
        )

@@

# ggsave(file.path(outdir, "fig1.png"))
ggsave(file.path(outdir, "fig1.pdf"), device = "pdf", height = 150, width = 180, units = "mm")
```

@@

marine_cap_stacked_bar <- marine_cap_sciname %>%
  mutate(common_name = case_when(
    common_name == "alaska pollock(=walleye poll.)" ~ "alaska pollock",
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    panel.spacing = unit(2, "mm"),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    # axis.text.y = element_text(size = 8),
    plot.margin = unit(c(0, 5, -5, -10), "mm")
  )

@@

marine_cap
```

@@

marine_aqua
```

@@

inland_cap_stacked_bar <- inland_cap_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile perch" ~ "\nnile perch",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.text.y.left = element_text(size = 8),
    strip.placement = "outside",
    legend.position = "none",
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    panel.spacing = unit(2, "mm"),
    plot.margin = margin(r = 5, l=-10, b=-5, unit="mm")# unit(c(, 5, 0, -10), "mm")
  )

@@

inland_aqua_stacked_bar <- inland_aqua_sciname %>%
  mutate(common_name = gsub(" nei", "", common_name)) %>%
  mutate(common_name = case_when(
    common_name == "ray-finned fishes" ~ "ray finned fishes",
    common_name == "striped catfish" ~ "\nstriped catfish",
    common_name == "freshwater siluroids" ~ "\nfreshwater siluroids",
    common_name == "nile tilapia" ~ "\nnile tilapia",
    TRUE ~ common_name
  )) %>%
  mutate(common_name = gsub(" ", "\n", common_name)) %>%
  mutate(common_name = reorder(common_name, desc(total))) %>%
  mutate(region = case_when(
    region == "North America" ~ "N. America",
    region == "South America" ~ "S. America",
    TRUE ~ region
  )) %>%
  ggplot(aes(x = consumption_live_t/consumption_live_magnitude, y = flow, fill = region)) +
  geom_bar(stat = "identity", position = "stack", width = 0.8) +
  scale_fill_manual(values = region6_palette) +
  labs(x = "", y = "", fill = "") +
  lims(x = c(stacked_bar_min, stacked_bar_max)) +
  facet_grid(vars(common_name), switch = "y") +
  theme_minimal() +
  theme(
    strip.placement = "outside",
    strip.text.y.left = element_text(size = 8),
    legend.position = "bottom",
    legend.box = "horizontal",
    legend.text = element_text(size = 8),
    legend.key.size = unit(3, "mm"),
    legend.box.margin = margin(l = -25, unit = "mm"),
    legend.margin = margin(t = -7, b = 0, unit = "mm"),
    panel.spacing = unit(2, "mm"),
    plot.margin = unit(c(0, 5, 0, -10), "mm")
  )

@@

@@

# ggsave(file.path(outdir, "fig2.png"), width = 9, height = 13, dpi = 500, unit = "in", device = "png")
ggsave(file.path(outdir, "fig2.pdf"), width = 180, height = 320, unit = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "fig3.png"))
ggsave(file.path(outdir, "fig3.pdf"), height = 180, width = 180, unit = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "fig4.png"))
ggsave(file.path(outdir, "fig4.pdf"), height = 180, width = 180, unit = "mm", device = "pdf")
```

@@

```{r regional_sankey, fig.height = 3, fig.width = 3}
regional_artis <- read.csv(file.path(datadir, "si_fig_1_data.csv")) %>%
  mutate(exporter_region = case_when(
    exporter_region == "North America" ~ "N.America",
    exporter_region == "South America" ~ "S.America",
    TRUE ~ exporter_region
  )) %>%
  mutate(importer_region = case_when(
    importer_region == "North America" ~ "N.America",
    importer_region == "South America" ~ "S.America",
    TRUE ~ importer_region
  ))

@@

marine_cap_regions$node <- factor(marine_cap_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "S.America", "N.America",
                                         "Africa"))

marine_cap_p <- marine_cap_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(t=-0.5, r=-7, b=-1, l=-25), unit = "mm")
    )

@@

marine_aqua_regions$node <- factor(marine_aqua_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "S.America", "N.America",
                                         "Africa"))

marine_aqua_p <- marine_aqua_regions %>%
  ggplot(aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               value = value,
               label = node)) +
    geom_sankey(flow.alpha = 0.6) +
    scale_fill_manual(values = region_colors) +
    geom_sankey_label(size = 4, color = "white", fill = "gray40") +
    theme_sankey(base_size = 18) +
  labs(x = NULL) +
    #labs(title = "Marine", x = NULL, y = "CAPTURE") +
  theme(
    legend.position = "none",
    axis.text.x = element_blank(),
    plot.title = element_text(hjust = 0.5),
    plot.margin = margin(c(t=-0.5, r=-7, b=-1, l=-25), unit = "mm")
    )

@@

inland_cap_regions$node <- factor(inland_cap_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "S.America", "N.America",
                                         "Africa"))

@@

inland_aqua_regions$node <- factor(inland_aqua_regions$node,
                              levels = c("Europe", "Oceania", "Asia",
                                         "S.America", "N.America",
                                         "Africa"))

@@

# ggsave(file.path(outdir, "si_fig1.png"))
ggsave(file.path(outdir, "si_fig1.pdf"), height = 200, width = 180, unit = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "si_fig2.png"))
ggsave(file.path(outdir, "si_fig2.pdf"), height = 200, width = 180, units = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "si_fig3.png"))
ggsave(file.path(outdir, "si_fig3.pdf"), height = 200, width = 180, units = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "si_fig4.png"))
ggsave(file.path(outdir, "si_fig4.pdf"), height = 200, width = 180, unit = "mm", device = "pdf")
```

@@

dom_source_by_habitat_method_p <- dom_source_by_habitat_method %>%
  mutate(habitat_method = gsub(" ", "\n", habitat_method)) %>%
  # Set factor levels
  mutate(habitat_method = factor(habitat_method, levels = c("marine\ncapture", "inland\ncapture",
                                                            "marine\naquaculture", "inland\naquaculture",
                                                            "unknown" ))) %>%
  ggplot(aes(x = year, y = live_weight_t / 1000000, fill = habitat_method)) +
  geom_area() +
  scale_fill_manual(values = habitat_source_colors) +
  theme_bw() +
  labs(x = "", y = "Live weight\nmillion tonnes", fill = "Source") +
  facet_wrap(~dom_source) +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 10),
    panel.spacing = unit(5, "mm"),
    legend.box.margin=margin(t = -15)
  )

@@

# ggsave(file.path(outdir, "si_fig5.png"))
ggsave(file.path(outdir, "si_fig5.pdf"), height = 125, width = 180, unit = "mm", device = "pdf")
```

@@

# ggsave(file.path(outdir, "si_fig6.png"))
ggsave(file.path(outdir, "si_fig6.pdf"), height = 80, width = 180, unit = "mm", device = "pdf")
```

@@

ggplot() +
  geom_line(data = artis_ts, aes(x = year, y = product_weight_t/1e6, color = hs_version), linetype = "dashed", linewidth = 1) +
  geom_line(data = custom_ts, aes(x = year, y = product_weight_t/1e6, color = hs_version), linewidth = 0.5, linetype = "solid") +
  scale_color_manual(
    values = c("Custom ARTIS Time series" = "black", "HS96" = "#741A32", "HS02" = "#B34232", "HS07" = "#D38F35", "HS12" = "red", "HS17" = "#114F59")
  ) +
  labs(x = "Year", y = "Product Weight (million tonnes)", color = "HS Version") +
  theme_bw() +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 10)
  )

# ggsave(file.path(outdir, "si_fig7.png"))
ggsave(file.path(outdir, "si_fig7.pdf"), height = 80, width = 180, unit = "mm", device = "pdf")
```
